---
title: "rr2 Solution"
author: "DJM"
date: "January 25, 2017"
output: html_document
---

2. Rename this file with your student ID or IDs (for easy grading).
1. Change the author to your name, or you and the friend with whom you are working.
3. Complete the three tasks below and push the Rmd back to Github.


## 1. Functions.

There are two functions below which have some missing lines. The first one should generate
data from a linear model. The second
should estimate the linear model from your data, and then make some plots to view your data.

Complete both functions where there are comments.

```{r functions}
generate.data <- function(n){
  X = matrix(rnorm(2*n), n, 2)
  epsilon = rnorm(n)
  beta = runif(3, -1, 1) 
  y = cbind(1, X) %*% beta + epsilon # how would you generate y from a linear model?
  df = data.frame(y=y, X1 = X[,1], X2 = X[,2])
  return(df)
}

estimate.and.plot <- function(dataframe, ...){
  mdl = lm(y~X1+X2, data=dataframe)
  resids = residuals(mdl) # how do you get residuals?
  fit =  fitted(mdl) # how do you get the fitted values?
  par(mfrow=c(2,2))
  with(dataframe, { ## Answer a question below about this line
    plot(y~fit, las=1, pch=19,...)
    plot(resids~X1, las=1, pch=19,...)
    plot(resids~X2, las=1, pch=19,...)
    })
  qqnorm(resids, pch=19, bty='n',las=1)
  qqline(resids)
  return(mdl)
}
```

## 2. Function execution.

```{r model-estimation, echo=FALSE, fig.align='center', fig.cap='Model Diagnostics'}
# 1. Use this chunk to generate some data with the first function. 
# 2. Estimate the model with the second function.
# 3. Uncomment the code below to include a table with coefficient 
#    estimates (replace mdl with the correct output from the second
#    function).

dataframe = generate.data(100)
mdl = estimate.and.plot(dataframe)
knitr::kable(summary(mdl)$coef, digits=3)
```

## 3. What does the `with` function do? Use `?with` to find out.

The function `with(df, code)` executes the code using the variables in the dataframe `df`. Much like
`lm` has a data argument, `with` basically allows you to provide data to any other block of code. For instance
`test = lm(y~X1+X2, data=mydata)` is the same as `with(mydata, {test=lm(y~X1+X2)})`.
