---
title: "rr2"
author: "Syaza Senin"
date: "January 25, 2017"
output: html_document
---

2. Rename this file with your student ID or IDs (for easy grading).
1. Change the author to your name, or you and the friend with whom you are working.
3. Complete the three tasks below and push the Rmd back to Github.


## 1. Functions.

There are two functions below which have some missing lines. The first one should generate
data from a linear model. The second
should estimate the linear model from your data, and then make some plots to view your data.

Complete both functions where there are comments.

```{r functions}
generate.data <- function(n){
  X = matrix(rnorm(2*n), n, 2)
  epsilon = rnorm(n)
  beta = runif(3, -1, 1) 
  y = cbind(1,X) %*% beta + epsilon
  df = data.frame(y=y, X1 = X[,1], X2 = X[,2])
  return(df)
}

estimate.and.plot <- function(dataframe, ...){
  mdl = lm(y~X1+X2, data=dataframe)
  resids = resid(mdl)
  fit =  fitted(mdl)
  par(mfrow=c(2,2))
  with(dataframe, {
    plot(y~fit, las=1, pch=19,...)
    plot(resids~X1, las=1, pch=19,...)
    plot(resids~X2, las=1, pch=19,...)
    })
  qqnorm(resids, pch=19, bty='n',las=1)
  qqline(resids)
  return(mdl)
}
```

## 2. Function execution.

```{r model-estimation, echo=FALSE, fig.align='center', fig.cap='Model Diagnostics'}
# 1. Use this chunk to generate some data with the first function. 
# 2. Estimate the model with the second function.
# 3. Uncomment the code below to include a table with coefficient 
#    estimates (replace mdl with the correct output from the second
#    function).

dataframe = generate.data(100)
mdl = estimate.and.plot(dataframe)
knitr::kable(summary(mdl)$coef, digits=3)
```

## 3. What does the `with` function do? Use `?with` to find out.

Perfom R expressions using the variables contained in a data frame


